Biogears in Anesthesia Screen Based Simulation

### 2016-02-17 paper_working_on/paper.tex
add two graph for bleeding out experiments

>>>>

\begin{figure}
  \centering
  \includegraphics[width=10cm]{bleeding_out_HeartRate_vs_Time.jpg}
  \caption{heart rate changes when patient bleeds out in Biogears simulation}
  \label{fig:patient bleeding}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=10cm]{bleeding_out_RespirationRate_vs_Time.jpg}
  \caption{heart rate changes when patient bleeds out in Biogears simulation}
  \label{fig:patient bleeding}
\end{figure}

In reality, it is not the case that patient could live with continuous hemorrhage: The heart rate of patient will increase because with blood loss there is not enough oxygen so his/her heart has to pump faster and absorb more oxygen. His respiratory rate will rise. But after a while, when he/she eventually loses
